Turtlebot SLAM

### 2013-01-22 Article/Article.tex
Changed the order of the subsections.
discussion and conclusion updated. Scan match reference added
Updated abstract

\begin{abstract}
Robots are used for a lot of tasks nowadays, to perform an assignment a robot needs a map of the environment. Using external referencing methods, like GPS, they can locate them self. Sometimes the maps are provided, making the task easier to perform. It becomes far more difficult when the robot has no map or external reference available. The task of mapping an environment can be split into two main components, namely exploration and SLAM which stands for Simultaneous Localization And Mapping. The exploration determines the path the robot takes to explore the unknown space of the environment. Exploration is based on the idea of frontiers, these are cells which separate unexplored cells from free explored cells. The exploration strategy then determines the next location the robot should move to. The SLAM part incorporates the new data as is becomes available when the robot moves to unexplored areas and takes measurements of previously unrecorded space. One intuitive way is to represent all the data as a graph where the nodes represent a pose of the robot and the edges connecting two nodes the measured constraints. The algorithm then tries to find a configuration of nodes which is maximally consistent with the constraints. This article will describe an implementation of this so called GraphSLAM with frontier exploration. All the implemented code is first tested and validated in a simulator and later run on a real robot, a TurtleBot.

@@

Exploration does not only consist of finding frontiers. Based on the frontiers a target location for the robot needs to be selected. Navigating to the closest frontier points is the simplest frontier-based exploration strategy. For this project, however, a more sophisticated implementation is chosen. Instead of sending the robot to the closest frontier point, a small search is performed to find suitable destinations. Generally, a small region around each frontier cell is searched. The goal is to give each frontier point a rating on how well it is suited as a destination. For this purposes an evaluation function has been implemented. It incorporates three features that are used to evaluate goals to be sent to the navigation stack. They are :
\begin{enumerate}
\item{Number of obstacles in the area}
\item{Distance to the previous goal}
\item{Distance between frontier and robot location}
\end{enumerate}
The first two features have a weight one, whereas the third is assigned a weight of five. This configuration turned out to create the best results (see Subsection \ref{sec:navEval}) The weighted sum of the features is used to find the goal to be sent to the navigation stack. This evaluation function enables the algorithm to select a reachable destination for the robot in almost every case. The frontier cells are sent to the move\_base in the order of the rating. When the navigation stack fails to steer the robot to a designated goal within a time constraint, the next best goal replaces the previous. The information gain is still next to optimal since the selected goal is preferred to be close to frontier points. At last the second feature makes sure that the robots path is smooth. Selecting a goal near the previous one makes the robot avoid too many loops in the emerging graph.
\subsection{Graph SLAM}
\label{sec:implSLAM}
The implemented Graph SLAM algorithm is based on \citep{Grisetti}. The graph consists of nodes representing poses along the robot trajectory. Odometry and sensor measurements are incorporated into the constraints contained in the edges. Similar to the Graph SLAM procedure explained in Section \ref{subsec:sotaSlam}, an edge connects two adjacent poses of the robot. 
\begin{figure}[h]
	\centering
		\includegraphics[width=0.50\textwidth]{figures/graph.png}
	\caption{An example of a simple graph (based on \citep{Grisetti}).}
	\label{fig:turtlebotexample_graph}
\end{figure}
When the graph is created the pose graph is optimized according to the constraints. This ``optimized" trajectory then determines the positions of obstacles on the map. The laser scan data are refined according to the poses they were obtained at. Each edge, thus, is labeled with the spatial difference between two poses \(x_i\) and \(x_j\). Let this error be denoted by \(e_{ij}(x_i, x_j)\). This information is obtained from a combination of odometry data and laser range sensor data. In fact, the raw odometry data is corrected using a laser scan matcher (see Subsection \ref{sec:scan}). 
Figure \ref{fig:turtlebotexample_graph} shows a sketch of a graph created by the algorithm. Two poses \(x_i\) and \(x_j\) are connected by an edge (Solid arrow). The ellipse at the top illustrates the label of the edge.

@@

>>>>

\begin{abstract}
To perform an assignment a robot needs a map of the environment, an added difficulty could be that the robot needs to build this map on his own. The task of mapping an environment can be split into two main components, namely exploration and SLAM which stands for Simultaneous Localization And Mapping. Exploration is based on the idea of frontiers, these are regions which separate unexplored space from free explored space, and a strategy determines to which frontier the robot moves next. SLAM incorporates the new data as it becomes available. One intuitive way is to represent all the data as a graph and then try to find a configuration of nodes which is maximally consistent with the constraints. This article will describe an implementation of this so called GraphSLAM with frontier exploration. All the implemented code is first tested and validated in a simulator and later run on a real robot, a TurtleBot.

@@

\subsection{Graph SLAM}
\label{sec:implSLAM}
The implemented Graph SLAM algorithm is based on \citep{Grisetti}. The graph consists of nodes representing poses along the robot trajectory. Odometry and sensor measurements are incorporated into the constraints contained in the edges. Similar to the Graph SLAM procedure explained in Section \ref{subsec:sotaSlam}, an edge connects two adjacent poses of the robot. 
\begin{figure}[h]
	\centering
		\includegraphics[width=0.50\textwidth]{figures/graph.png}
	\caption{An example of a simple graph (based on \citep{Grisetti}).}
	\label{fig:turtlebotexample_graph}
\end{figure}
When the graph is created the pose graph is optimized according to the constraints. This ``optimized" trajectory then determines the positions of obstacles on the map. The laser scan data are refined according to the poses they were obtained at. Each edge, thus, is labeled with the spatial difference between two poses \(x_i\) and \(x_j\). Let this error be denoted by \(e_{ij}(x_i, x_j)\). This information is obtained from a combination of odometry data and laser range sensor data. In fact, the raw odometry data is corrected using a laser scan matcher (see Subsection \ref{sec:scan}). 
Figure \ref{fig:turtlebotexample_graph} shows a sketch of a graph created by the algorithm. Two poses \(x_i\) and \(x_j\) are connected by an edge (Solid arrow). The ellipse at the top illustrates the label of the edge.

@@

Exploration does not only consist of finding frontiers. Based on the frontiers a target location for the robot needs to be selected. Navigating to the closest frontier points is the simplest frontier-based exploration strategy. For this project, however, a more sophisticated implementation is chosen. Instead of sending the robot to the closest frontier point, a small search is performed to find suitable destinations. Generally, a small region around each frontier cell is searched. The goal is to give each frontier point a rating on how well it is suited as a destination. For this purposes an evaluation function has been implemented. It incorporates three features that are used to evaluate goals to be sent to the navigation stack. They are :
\begin{enumerate}
\item{Number of obstacles in the area}
\item{Distance to the previous goal}
\item{Distance between frontier and robot location}
\end{enumerate}
The first two features have a weight one, whereas the third is assigned a weight of five. This configuration turned out to create the best results (see Subsection \ref{sec:navEval}) The weighted sum of the features is used to find the goal to be sent to the navigation stack. This evaluation function enables the algorithm to select a reachable destination for the robot in almost every case. The frontier cells are sent to the move\_base in the order of the rating. When the navigation stack fails to steer the robot to a designated goal within a time constraint, the next best goal replaces the previous. The information gain is still next to optimal since the selected goal is preferred to be close to frontier points. At last the second feature makes sure that the robots path is smooth. Selecting a goal near the previous one makes the robot avoid too many loops in the emerging graph.
